### 2015-04-29 inst/vign/taxize_vignette.Rmd

[eol]: http://eol.org/
[taxosaurus]: http://api.phylotastic.org/tnrs
[ncbi]: http://www.ncbi.nlm.nih.gov/
[itis]: http://www.itis.gov/
[phylomatic]: http://phylodiversity.net/phylomatic/
[opentree]: http://blog.opentreeoflife.org/
[wikispecies]: http://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/
[iucn]: http://www.iucnredlist.org/

>>>>

[eol]: http://www.eol.org/
[taxosaurus]: http://api.phylotastic.org/tnrs
[ncbi]: http://www.ncbi.nlm.nih.gov/
[itis]: http://www.itis.gov/
[phylomatic]: http://phylodiversity.net/phylomatic/
[opentree]: http://blog.opentreeoflife.org/
[wikispecies]: http://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/
[iucn]: http://www.iucnredlist.org/
